LAs_clusters

### 2020-12-02 src/LAs_Clusters.Rmd
regressions with nvq4

labour <- labour %>%
  dplyr::select(GEOGRAPHY_CODE, GEOGRAPHY_NAME, VARIABLE_NAME, OBS_VALUE) %>%
  distinct(GEOGRAPHY_CODE, VARIABLE_NAME, .keep_all = T) %>% 
  spread(VARIABLE_NAME, OBS_VALUE) %>% 
  rename(lad19cd = GEOGRAPHY_CODE) %>%
  rename(managers =  `% all in employment who are - 1: managers, directors and senior officials (SOC2010)`) %>%
  rename(prof = `% all in employment who are - 2: professional occupations (SOC2010)`) %>%
  rename(tech = `% all in employment who are - 3: associate prof & tech occupations (SOC2010)`) %>%
  rename(admin = `% all in employment who are - 4: administrative and secretarial occupations (SOC2010)`) %>%
  rename(skilled = `% all in employment who are - 5: skilled trades occupations (SOC2010)`) %>%
  rename(caring = `% all in employment who are - 6: caring, leisure and other service occupations (SOC2010)`) %>%
  rename(sales = `% all in employment who are - 7: sales and customer service occupations (SOC2010)`) %>%
  rename(plant = `% all in employment who are - 8: process, plant and machine operatives (SOC2010)`) %>%
  rename(elementary = `% all in employment who are - 9: elementary occupations (SOC2010)`) %>%
  rename(NVQ3 = `% with NVQ3+ - aged 16-64`) %>%
  rename(NVQ4 = `% with NVQ4+ - aged 16-64`) %>%
  rename(econ.act = `Economic activity rate - aged 16-64`)

@@

@@

```{r}
data <- list(lad, ladDist, job.dens, pop, pop.dens, labour, earnings, busi) # ns 
sapply(data, function(x) dim(x))
sapply(data, function(x) names(x))

@@

aux <- multinom(cluster.up ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)
                             , round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs
                            , n.obs, n.obs))))

@@

aux <- multinom(cluster.tests ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs))))

@@

aux <- multinom(cluster.down ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs))))

>>>>

labour <- labour %>%
  dplyr::select(GEOGRAPHY_CODE, GEOGRAPHY_NAME, VARIABLE_NAME, OBS_VALUE) %>%
  distinct(GEOGRAPHY_CODE, VARIABLE_NAME, .keep_all = T) %>% 
  spread(VARIABLE_NAME, OBS_VALUE) %>% 
  rename(lad19cd = GEOGRAPHY_CODE) %>%
  rename(managers =  `% all in employment who are - 1: managers, directors and senior officials (SOC2010)`) %>%
  rename(prof = `% all in employment who are - 2: professional occupations (SOC2010)`) %>%
  rename(tech = `% all in employment who are - 3: associate prof & tech occupations (SOC2010)`) %>%
  rename(admin = `% all in employment who are - 4: administrative and secretarial occupations (SOC2010)`) %>%
  rename(skilled = `% all in employment who are - 5: skilled trades occupations (SOC2010)`) %>%
  rename(caring = `% all in employment who are - 6: caring, leisure and other service occupations (SOC2010)`) %>%
  rename(sales = `% all in employment who are - 7: sales and customer service occupations (SOC2010)`) %>%
  rename(plant = `% all in employment who are - 8: process, plant and machine operatives (SOC2010)`) %>%
  rename(elementary = `% all in employment who are - 9: elementary occupations (SOC2010)`) %>%
  rename(NVQ3 = `% with NVQ3+ - aged 16-64`) %>%
  rename(NVQ4 = `% with NVQ4+ - aged 16-64`) %>%
  rename(econ.act = `Economic activity rate - aged 16-64`) %>% # No NVQ data here as this is for Jul 2019-Jun 2020. NVQ is only  
  dplyr::select(-NVQ3, -NVQ4)                                  # available for Dec - Dec. I download these data seperetely.

@@

nvq4 <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_17_5.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1807745025...1807745028,1807745030...1807745032,1807745034...1807745155,1807745157...1807745164,1807745166...1807745170,1807745172...1807745177,1807745179...1807745194,1807745196,1807745197,1807745199,1807745201...1807745218,1807745221,1807745222,1807745224,1807745226...1807745231,1807745233,1807745234,1807745236...1807745244&date=latestMINUS2&variable=290&measures=20599,21001,21002,21003")

nvq4 <- nvq4 %>%
  dplyr::select(GEOGRAPHY_CODE, GEOGRAPHY_NAME, MEASURES_NAME, OBS_VALUE) %>%
  filter(MEASURES_NAME=="Variable") %>%
  dplyr::select(-MEASURES_NAME) %>%
  distinct(GEOGRAPHY_CODE, OBS_VALUE, .keep_all = T) %>% 
  rename(lad19cd = GEOGRAPHY_CODE) %>%
  rename(nvq4 = OBS_VALUE)
```

@@

```{r}
data <- list(lad, ladDist, job.dens, pop, pop.dens, labour, earnings, busi, nvq4) # ns 
sapply(data, function(x) dim(x))
sapply(data, function(x) names(x))

@@

aux <- multinom(cluster.up ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) + nvq4 +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)
                             , round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs
                            , n.obs, n.obs))))

@@

aux <- multinom(cluster.tests ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south + nvq4 +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs))))

@@

aux <- multinom(cluster.down ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) + nvq4 +
                  I(LAD.tests.am20/pop) + # non sensitive to addition of other tests pm
                  virgin
                , data = data, 
                trace = F) # to avoid messages

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "% of NVQ4+",
                             "n. of AM broadband tests per hab., 2019",
                             "% of Virgin Media connections"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs))))
